---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# underground

**Updated on `r Sys.Date()` with data up to 2018-08-18**

London Underground performance data is published in
[spreadsheets](https://tfl.gov.uk/corporate/publications-and-reports/underground-services-performance).
This R package makes it available in [csv
files](https://github.com/nacnudus/underground/tree/master/inst/extdata), or in
an R data frame.

The secret sauce is [tidyxl](https://nacnudus.github.io/tidyxl) with a dash of
[unpivotr](https://nacnudus.github.io/unpivotr).

## Installation

```r
devtools::install_github("nacnudus/underground")
```

## Example

```{r}
library(underground)
library(dplyr)
library(ggplot2)

underground %>%
  filter(metric == "Train delays longer than 15 minutes",
         year == "2018/19",
         is.na(quarter),
         period == 5,
         line != "All Lines") %>%
  mutate(fill= underground_colours[line]) %>%
  select(line, value, fill) %>%
  ggplot(aes(line, value, fill = fill)) +
  geom_bar(stat = "identity") +
  scale_fill_identity("", labels = underground_lines, guide = "legend") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  xlab("") +
  ylab("") +
  ggtitle("Train delays longer than 15 minutes",
          subtitle = "Period 5 2018/19 from 21 July to 17 August 2018")
```

## Control periods

Most series are reported in 'periods' approximately four weeks long, used by the
whole UK rail industry.  Some periods are shorter or longer so that each year is
covered by exactly 13 periods, beginning on the April the 1st.

Join the dataset `rail_periods` to resolve periods (1 to 13) to dates.

## Metrics

```{r}
distinct(underground, metric) %>%
  pull(metric)
```
